Enhancement of SDR in Thessaloniki

### 2024-01-15 GHI_enh_03_process.tex
Commit 2024-01-15 13:17

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.mean)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.sum)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.max)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.N)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   ,}\AttributeTok{.smooth=}\NormalTok{T, }\AttributeTok{.smooth\_span =} \FloatTok{0.3}\NormalTok{, }\AttributeTok{.interactive =}\NormalTok{ F)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_acf\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{F, }\AttributeTok{.lags =}\DecValTok{1}\SpecialCharTok{:}\DecValTok{60}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-14} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_stl\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N,}
                     \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"observed"}\NormalTok{,}\StringTok{"season"}\NormalTok{, }\StringTok{"trend"}\NormalTok{, }\StringTok{"remainder"}\NormalTok{),}
                     \AttributeTok{.trend =} \DecValTok{180}\NormalTok{,}
                     \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
                     \AttributeTok{.interactive =}\NormalTok{ F}
\NormalTok{                     )}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
frequency = 30 observations
\end{verbatim}

\begin{verbatim}
trend = 180 observations
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-15} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_stl\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N,}
                     \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"observed"}\NormalTok{,}\StringTok{"season"}\NormalTok{, }\StringTok{"trend"}\NormalTok{, }\StringTok{"remainder"}\NormalTok{),}
                     \AttributeTok{.trend =} \DecValTok{180}\NormalTok{,}
                     \AttributeTok{.frequency =} \DecValTok{30}\NormalTok{,}
                     \AttributeTok{.interactive =}\NormalTok{ F}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
frequency = 30 observations
trend = 180 observations
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-16} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_daily, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ F,}
                          \AttributeTok{.feature\_set =} \FunctionTok{c}\NormalTok{(}\StringTok{"week"}\NormalTok{, }\StringTok{"month.lbl"}\NormalTok{, }\StringTok{"quarter"}\NormalTok{, }\StringTok{"year"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-17} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_seasonal\_diagnostics}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N, }\AttributeTok{.interactive =}\NormalTok{ F)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-18} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# https://business{-}science.github.io/timetk/articles/TK08\_Automatic\_Anomaly\_Detection.html}

\FunctionTok{plot\_time\_series\_regression}\NormalTok{(}
    \AttributeTok{.data         =}\NormalTok{ ST\_E\_monthly,}
    \AttributeTok{.date\_var     =}\NormalTok{ Date,}
    \AttributeTok{.formula      =}\NormalTok{ wattGLB.N }\SpecialCharTok{\textasciitilde{}} \FunctionTok{as.numeric}\NormalTok{(Date)  ,}
    \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
    \CommentTok{\# .interactive  = FALSE,}
    \AttributeTok{.show\_summary =} \ConstantTok{TRUE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}

Call:
stats::lm(formula = .formula, data = df)

Residuals:
   Min     1Q Median     3Q    Max 
-404.5 -198.5  -82.3  139.7 1090.3

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -7.444e+01  6.622e+01  -1.124    0.262    
as.numeric(Date)  3.317e-07  5.344e-08   6.207 1.51e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 276.5 on 353 degrees of freedom
Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-19} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{lm1 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(ST\_E\_monthly}\SpecialCharTok{$}\NormalTok{wattGLB.N }\SpecialCharTok{\textasciitilde{}}\NormalTok{ ST\_E\_monthly}\SpecialCharTok{$}\NormalTok{Date)}
\FunctionTok{summary}\NormalTok{(lm1)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}

Call:
lm(formula = ST_E_monthly$wattGLB.N ~ ST_E_monthly$Date)

Residuals:
   Min     1Q Median     3Q    Max 
-404.5 -198.5  -82.3  139.7 1090.3

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -7.444e+01  6.622e+01  -1.124    0.262    
ST_E_monthly$Date  3.317e-07  5.344e-08   6.207 1.51e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 276.5 on 353 degrees of freedom
Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series\_regression}\NormalTok{(}
    \AttributeTok{.data         =}\NormalTok{ ST\_E\_daily,}
    \AttributeTok{.date\_var     =}\NormalTok{ Date,}
    \AttributeTok{.formula      =}\NormalTok{ wattGLB.N }\SpecialCharTok{\textasciitilde{}} \FunctionTok{as.numeric}\NormalTok{(Date)  ,}
    \AttributeTok{.facet\_ncol   =} \DecValTok{2}\NormalTok{,}
    \CommentTok{\# .interactive  = FALSE,}
    \AttributeTok{.show\_summary =} \ConstantTok{FALSE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-6-20} \end{center}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#  Save from environment  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\DocumentationTok{\#\# Variables}
\NormalTok{objects }\OtherTok{\textless{}{-}} \FunctionTok{grep}\NormalTok{(}\StringTok{"\^{}tic$|\^{}tac$|\^{}Script.Name$|\^{}tag$"}\NormalTok{, }\FunctionTok{ls}\NormalTok{(), }\AttributeTok{value =}\NormalTok{ T, }\AttributeTok{invert =}\NormalTok{ T)}
\NormalTok{objects }\OtherTok{\textless{}{-}}\NormalTok{ objects[}\FunctionTok{sapply}\NormalTok{(objects, }\ControlFlowTok{function}\NormalTok{(x)}
    \FunctionTok{is.numeric}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{|}
        \FunctionTok{is.character}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{\&}
        \FunctionTok{object.size}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{\textless{}} \DecValTok{1009} \SpecialCharTok{\&}
\NormalTok{        (}\SpecialCharTok{!}\FunctionTok{is.vector}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{|}
             \SpecialCharTok{!}\FunctionTok{is.function}\NormalTok{(}\FunctionTok{get}\NormalTok{(x))), }\AttributeTok{simplify =}\NormalTok{ T)]}
\DocumentationTok{\#\# Data}
\NormalTok{objects }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}
\NormalTok{    objects,}
    \FunctionTok{grep}\NormalTok{(}\StringTok{"\^{}ST\_"}\NormalTok{, }\FunctionTok{ls}\NormalTok{(), }\AttributeTok{value =} \ConstantTok{TRUE}\NormalTok{)}
\NormalTok{)}

@@

\begin{verbatim}
2024-01-15 09:05:38.4 athan@sagan GHI_enh_03_process.R 1.420055 mins
\end{verbatim}

>>>>

interactive FALSE

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.mean, }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Warning: Removed 2 rows containing missing values (`geom_line()`).
Removed 2 rows containing missing values (`geom_line()`).
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.sum , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Warning: Removed 2 rows containing missing values (`geom_line()`).
Removed 2 rows containing missing values (`geom_line()`).
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.max , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Warning: Removed 2 rows containing missing values (`geom_line()`).
Removed 2 rows containing missing values (`geom_line()`).
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_daily, Date, wattGLB.N   , }\AttributeTok{.interactive =}\NormalTok{ isinter)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot\_time\_series}\NormalTok{(ST\_E\_monthly, Date, wattGLB.N   , }\AttributeTok{.smooth =}\NormalTok{ T, }\AttributeTok{.smooth\_span =} \FloatTok{0.3}\NormalTok{ )}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#}
\CommentTok{\#}
\CommentTok{\# plot\_acf\_diagnostics(ST\_E\_daily, Date, wattGLB.N, .interactive = F, .lags = 1:60)}
\CommentTok{\#}
\CommentTok{\#}
\CommentTok{\#}
\CommentTok{\# plot\_stl\_diagnostics(ST\_E\_daily, Date, wattGLB.N,}
\CommentTok{\#                      .feature\_set = c("observed","season", "trend", "remainder"),}
\CommentTok{\#                      .trend = 180,}
\CommentTok{\#                      .frequency = 30,}
\CommentTok{\#                      .interactive = F}
\CommentTok{\#                      )}
\CommentTok{\#}
\CommentTok{\# plot\_stl\_diagnostics(ST\_E\_monthly, Date, wattGLB.N,}
\CommentTok{\#                      .feature\_set = c("observed","season", "trend", "remainder"),}
\CommentTok{\#                      .trend = 180,}
\CommentTok{\#                      .frequency = 30,}
\CommentTok{\#                      .interactive = F}
\CommentTok{\# )}
\CommentTok{\#}
\CommentTok{\#}
\CommentTok{\# plot\_seasonal\_diagnostics(ST\_E\_daily, Date, wattGLB.N, .interactive = F,}
\CommentTok{\#                           .feature\_set = c("week", "month.lbl", "quarter", "year"))}
\CommentTok{\#}
\CommentTok{\# plot\_seasonal\_diagnostics(ST\_E\_monthly, Date, wattGLB.N, .interactive = F)}
\CommentTok{\#}
\CommentTok{\# \# https://business{-}science.github.io/timetk/articles/TK08\_Automatic\_Anomaly\_Detection.html}
\CommentTok{\#}
\CommentTok{\# plot\_time\_series\_regression(}
\CommentTok{\#     .data         = ST\_E\_monthly,}
\CommentTok{\#     .date\_var     = Date,}
\CommentTok{\#     .formula      = wattGLB.N \textasciitilde{} as.numeric(Date)  ,}
\CommentTok{\#     .facet\_ncol   = 2,}
\CommentTok{\#     \# .interactive  = FALSE,}
\CommentTok{\#     .show\_summary = TRUE}
\CommentTok{\# )}
\CommentTok{\# lm1 \textless{}{-} lm(ST\_E\_monthly$wattGLB.N \textasciitilde{} ST\_E\_monthly$Date)}
\CommentTok{\# summary(lm1)}
\CommentTok{\#}
\CommentTok{\# plot\_time\_series\_regression(}
\CommentTok{\#     .data         = ST\_E\_daily,}
\CommentTok{\#     .date\_var     = Date,}
\CommentTok{\#     .formula      = wattGLB.N \textasciitilde{} as.numeric(Date)  ,}
\CommentTok{\#     .facet\_ncol   = 2,}
\CommentTok{\#     \# .interactive  = FALSE,}
\CommentTok{\#     .show\_summary = FALSE}
\CommentTok{\# )}

\CommentTok{\#  Save from environment  {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\DocumentationTok{\#\# Variables}
\NormalTok{objects }\OtherTok{\textless{}{-}} \FunctionTok{grep}\NormalTok{(}\StringTok{"\^{}tic$|\^{}tac$|\^{}Script.Name$|\^{}tag$"}\NormalTok{, }\FunctionTok{ls}\NormalTok{(), }\AttributeTok{value =}\NormalTok{ T, }\AttributeTok{invert =}\NormalTok{ T)}
\NormalTok{objects }\OtherTok{\textless{}{-}}\NormalTok{ objects[}\FunctionTok{sapply}\NormalTok{(objects, }\ControlFlowTok{function}\NormalTok{(x)}
    \FunctionTok{is.numeric}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{|}
        \FunctionTok{is.character}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{\&}
        \FunctionTok{object.size}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{\textless{}} \DecValTok{1009} \SpecialCharTok{\&}
\NormalTok{        (}\SpecialCharTok{!}\FunctionTok{is.vector}\NormalTok{(}\FunctionTok{get}\NormalTok{(x)) }\SpecialCharTok{|}
             \SpecialCharTok{!}\FunctionTok{is.function}\NormalTok{(}\FunctionTok{get}\NormalTok{(x))), }\AttributeTok{simplify =}\NormalTok{ T)]}
\DocumentationTok{\#\# Data}
\NormalTok{objects }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}
\NormalTok{    objects,}
    \FunctionTok{grep}\NormalTok{(}\StringTok{"\^{}ST\_"}\NormalTok{, }\FunctionTok{ls}\NormalTok{(), }\AttributeTok{value =} \ConstantTok{TRUE}\NormalTok{)}
\NormalTok{)}

@@

\begin{verbatim}
2024-01-15 10:23:12.5 athan@sagan GHI_enh_03_process.R 1.167804 mins
\end{verbatim}
